The Effect of Events on Australian Parliamentary Discussion (1870--2017)

### 2018-09-30 outputs/docs/events/svm-rmarkdown-article-example.tex
Improve paper

\setcounter{secnumdepth}{0}

@@

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 29
September 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Monica Alexander (University of Toronto) and Rohan Alexander (Australian National University)},
             pdfkeywords = {text analysis, politics, Australia},  
            pdftitle={Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\noindent Government policy is partly driven by parliamentary discussion.
Conversely, that same discussion can indicate a government's priorities.
But major events--both expected, such as an election, and unexpected,
such as a recession or terrorist attack--can affect the course of
parliamentary discussion. In this paper, we systematically analyse how
parliamentary discussion changes in response to different types of
events in Australian history. We compile a dataset of what was said in
Australian state and federal parliaments from the mid-1800s through to
2017 based on available public records. We use a structural text model
to reduce the dimensionality of the text and to impose prior knowledge
such as correlation between days and changes over time. We then examine
the effect of various events. We find that: 1) changes of government are
associated with topic changes only when there is also a change of the
party in power; and 2) economic events, such as financial crises, have
significant and persistent effects. Our findings have implications for
how we think about the longer-term trajectory of government policy as
the media cycle becomes increasingly focused on short-term events.

@@

New governments often go to some trouble to be different to the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by his predecessor John Howard,
and then one of Tony Abbott's first acts was to repeal his predecessor
Kevin Rudd's carbon tax. Similarly, significant events such as the 9/11
attacks or the Great Recession have often altered the course of a
government. However it is not so clear which events drive changes, for
how long these changes persist, and what was given up due to the change.

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016}
for dimensionality reduction and to impose structure such as correlation
between days and changes over time. We then examine changes at various
types of events, including: changes in government; changes in the
political environment (as defined by polling or other results); changes
in economic conditions; and other significant events (such as the 9/11
attacks or the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale
parliamentary text records from multiple Australian parliaments. Our
work fits into a growing literature that considers text as an input to
more usual quantitative techniques, rather than requiring separate
analysis. While using text as data has well-known shortcomings, it
allows larger-scale analysis that would not be viable using
less-automated approaches and so it can identify patterns that may
otherwise be overlooked.

@@

Following the example of the UK a daily text record called Hansard of
what was said in Australian parliaments has been made available since
their establishment.\footnote{While Hansard is not necessarily verbatim,
  it is considered close enough for text-as-data purposes. For instance,
  \citet{Mollin2008} found that in the case of the UK Hansard the
  differences would only affect specialised linguistic analysis.
  \citet{Edwards2016} examined Australia, New Zealand and the UK, and
  found that changes were usually made by those responsible for creating
  the Hansard record, instead of the parliamentarians.} Earlier work on
the influence of parliaments, such as \citet{ZandenBuringhBosker2012} or
\textbf{{[}ANOTHER REFERENCE - Maybe Frank Fisher `Reframing Public
Policy'?{]}}, often examined broader activity measures such as counts of
sitting days. This allowed for long time frames and wide comparisons.
But analysing Hansard records and their equivalents directly are an
increasingly viable and popular source of data as new methods and
reduced computational costs make larger-scale analysis easier,
complementing other measures.

The digitisation of the Canadian Hansard, \citet{BeelenEtc2017}, allowed
\citet{RheaultCochran2018} to examine ideology and party polarisation in
Britain and Canada. In the UK, \citet{Duthie2016} analysed Hansard
records to examine which politicians made supportive or aggressive
statements toward other politicians between 1979 and 1990 and
\citet{PetersonSpirling2018} examined polarisation. And as digitisation
methods improve older UK records can be analysed, for instance
\citet{Dimitruk2018} considers the effect of estate bills on
prorogations in seventeenth century England. In New Zealand,
\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
and \citet{Graham2016} examined unparliamentary language between 1890
and 1950. And in the US \citet{GentzkowShapiroTaddy2018} examine
congressional speech records from 1873 to 2016 to find that partisanship
has risen in the past few decades.

@@

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
An example of what a page of Hansard looks like is included in Appendix
\textbf{{[}ADD NUMBERING{]}}. There is a more limited set of XML records
available in some cases.\footnote{Tim Sherratt makes these XML records
  available as a single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through to today from Open Australia's website. The
  records can also be downloaded from the Australian Hansard website.}
There are 65,000 \textbf{{[}UPDATE{]}} Hansard records publicly
available across the state and federal parliaments (Table
\ref{tab:yearsusedtable}) \textbf{{[}UPDATE NUMBERING{]}}. As with any
larger-scale data process, there are various issues with some of the
PDFs and the known ones are detailed in Appendix \textbf{{[}ADD
NUMBERING{]}}.\footnote{The NSW Legislative Council was established
  earlier than 1856, however the earlier Hansard records have not been
  through an independent OCR process and were not used in this paper.
  However, the Google Tesseract OCR engine as implemented by
  \citet{Ooms2018tesseract} provided useful data and these could be used
  in the future.}

@@

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in Appendix \textbf{{[}ADD
  NUMBERING{]}}.} These scripts are primarily based on: the
\texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified. One way to provide assurance that
mistakes in older records are not driving the results is to analyse the
percentage of stop-words in each record over time. This details of this
are provided in Appendix \textbf{{[}ADD NUMBERING{]}} and suggest that
there is no significant difference in the quality of the parsing over
time. The \texttt{hunspell} package of \citet{Ooms2017} is also used to
help find spelling issues.

These daily records are the main level at which we consider the data in
this paper, but the daily records are also further divided into
individual-level records. Sometimes these are just short interjections
or notes that are not specific to any particular politician, such as
`Honourable members interjecting'. The high dimensional nature of text
data means that the appropriate analysis data are research-question
specific and datasets need to be tidied toward that. For instance, in
our paper interjections are not important because they do not usually
contribute much to defining the topics being discussed. But they are
interesting in their own right and \citet{Whyte2017} analysed them in a
Canadian context for the period 1926 to 2015 to find that female MPs
were more likely to be interrupted than male MPs.

Usually the disaggregation into individual-level records is done by
identifying politicians' names in particular patterns. For instance,
when Hansard is indicating that a particular person is speaking, as
opposed to being mentioned (for more on the political effect of being
mentioned see \citet{Alexander2018}), often the name is in upper case,
for instance `Mr WHITLAM' or `Mr MENZIES'; followed by a dash or colon;
or are next to some title within brackets. There is substantial
variation in how the person making a statement is identified. Again some
error is introduced at this stage because of inconsistencies over time
and between the parliaments. There is considerable variance but on
average each daily record had 250 \textbf{{[}UPDATE{]}} individual-level
records, resulting in roughly 15 million rows \textbf{{[}UPDATE{]}}
across the state and federal parliaments.

Text usually needs to be pre-processed before topic models can be used.
The specific steps that we take are to remove numbers and punctuation
and to change all the words to lower case. Then the sentences are
deconstructed and each word considered individually. In addition to the
packages already mentioned, in this step the R scripts to do this use
the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
\textbf{{[}Need to bundle\_ngrams i.e.~New Zealand is new\_zealand.{]}}

@@

Data from other sources are useful to complement the parliamentary text
data. For instance, although the name, party, and division represented
are contained in Hansard records they are inconsistent. Also non-Hansard
information about the politicians informs our analysis. This includes:
date of birth and date of death; sex; date of entry to parliament and
exit from parliament; some aspects of their pre- and post-parliamentary
career; some aspects of their parliamentary career, such as ministry
appointments; and electoral information such as primary and
two-party-preferred results.

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments. However these had many
errors and were supplemented by data from the Australian Dictionary of
Biography and Wikipedia.\footnote{An example of the additional
  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}.} The
source for the electoral results is the Australian Electoral Commission
and Adam Carr's Australian Election Archive.

@@

The main model that we use in this paper is the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. In a similar way to
\citet{MuellerRauh2018}, we use these topics to analyse the effect of
various events. In Appendix \textbf{{[}ADD NUMBERING{]}}, we include an
alternative approach that follows \citet{Taddy2015} by using word2vec,
which more closely uses words, rather than topics, as an input.

The basis of the STM is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section we provide a brief overview of
both the LDA model and the STM. We consider the outputs of the topic
model as reduced dimension inputs that can be analysed.

@@

As applied to Hansard, the LDA method considers each statement to be a
result of a process where a politician first chooses the topics they
want to speak about. After choosing the topics, the speaker then chooses
appropriate words to use for each of those topics. More generally, the
LDA topic model works by considering each document as having been
generated by some probability distribution over topics. Similarly, each
topic could be considered a probability distribution over terms. To
choose the terms used in each document the speaker picks terms from each
topic in the appropriate proportion. Figures
\ref{fig:topicsoverdocuments} and \ref{fig:topicsoverterms} in Appendix
\textbf{{[}ADD NUMBERING{]}} illustrates an example with five topics,
two documents, and ten terms.

@@

Gibbs sampling or the variational expectation-maximization algorithm can
be used to approximate the posterior. A summary of these approaches is
provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The choice of the
number of topics, \emph{k}, drives the results and must be specified
\emph{a priori}. If there is a strong reason for a particular number,
then this can be used. Otherwise, one way to choose an appropriate
number is to use cross validation.

@@

We primarily implement the STM on the daily-level parliamentary text
data described earlier using the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. We consider both topic prevalence
and content to be functions of time. The choice of the number of topics
to use in the model is a situation-specific compromise. We use standard
diagnostic techniques with cross validation to decide on 80
\textbf{{[}UPDATE AS APPROPRIATE{]}} topics. More detail on this
selection process is available in Appendix \textbf{{[}ADD NUMBERING{]}}.

@@

We are interested in the effect of political, economic, and other events
on Australian parliamentary discussion. Political events are those
related to a change of government or an election. Economic events are
defined by substantial changes in various economic measures, such as the
onset of the Great Depression or the Great Recession. Other events are
those such as the 9/11 attacks, or the Bali Bombing. The full list of
events that we consider is detailed in Appendix \textbf{{[}ADD
NUMBERING{]}}.

@@

\section{Appendix}\label{appendix}

\subsection{Example page}\label{example-page}

@@

\subsection{Document sources}\label{document-sources}

\subsection{Dataset issues}\label{dataset-issues}

@@

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright\strut
year\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
I have this number in Reps\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
They say this number in Senate\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
They say this number in Reps\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright\strut
Difference in Reps\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Comment\strut
\end{minipage} & \begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
Source\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1902\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
106\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
93\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
107\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Positive means I am missing some\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\url{https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear}\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1908\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
93\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
84\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
91\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-2\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Negative means I have too many\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1909\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
97\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
71\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
98\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1918\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
87\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
68\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
86\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1920\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
113\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
76\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
114\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1921\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
92\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
79\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
93\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1934\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
36\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
22\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
35\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1935\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
54\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
37\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
55\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1942\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
44\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
36\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
45\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1948\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
89\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
39\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
90\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1951\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
55\strut

>>>>

% This controls whether you get numbers in the sections or not
% \setcounter{secnumdepth}{0}

@@

\title{The Effect of Events on Australian Parliamentary Discussion (1870--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 30
September 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Monica Alexander (University of Toronto) and Rohan Alexander (Australian National University)},
             pdfkeywords = {text analysis, politics, Australia},  
            pdftitle={The Effect of Events on Australian Parliamentary Discussion (1870--2017)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\noindent We systematically analyse how parliamentary discussion changes in
response to different types of events in Australian history. We first
compile a dataset of what was said in Australian state and federal
parliaments from the mid-1800s through to 2017 based on available public
records. We then use a structural text model to reduce the
dimensionality of the text and to impose prior knowledge such as
correlation between days and changes over time. Finally, we examine the
effect of various events using a Bayesian choice model. We find that: 1)
elections are associated with topic changes only when the party in power
changes but a change in government sometimes does not require this to be
associated with topic changes; and 2) economic events, such as financial
crises, have less significant and persistent effects than other events
such as terrorism. Our findings have implications for how we think about
the longer-term trajectory of government policy as the media cycle
becomes increasingly focused on short-term events.

@@

Government policy is partly driven by parliamentary discussion.
Conversely, that same discussion can indicate a government's priorities.
But major events--both expected, such as an election, and unexpected,
such as a recession or terrorist attack--can affect the course of
parliamentary discussion. For instance, new governments often go to some
trouble to be different to the governments they replace, such as Kevin
Rudd's apology to Indigenous Australians not being supported by his
predecessor John Howard, and then one of Tony Abbott's first acts was to
repeal his predecessor Kevin Rudd's carbon tax. Similarly, significant
events such as the 9/11 attacks or the Great Recession have often
altered the course of a government. But it is not so clear which events
drive changes, for how long these changes persist, and what was given up
due to the change.

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016}
for dimensionality reduction and to impose structure such as correlation
between days and changes over time. We then use a simple discrete choice
model to examine changes at various types of events, including: changes
in government; changes in the political environment (as defined by
polling or other results); changes in economic conditions; and other
significant events (such as the 9/11 attacks or the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale
parliamentary text records from multiple Australian parliaments. Our use
of a discrete choice model - essentially a time series multinomial model
of choices - allows us to construct a counterfactual. Our work fits into
a growing literature that considers text as an input to more usual
quantitative techniques, rather than requiring separate analysis. While
using text as data has well-known shortcomings, it allows larger-scale
analysis that would not be viable using less-automated approaches and so
it can identify patterns that may otherwise be overlooked.

@@

Following the example of the UK a daily text record called Hansard of
what was said in Australian parliaments has been made available since
their establishment.\footnote{While Hansard is not necessarily verbatim,
  it is considered close enough for text-as-data purposes. For instance,
  \citet{Mollin2008} found that in the case of the UK Hansard the
  differences would only affect specialised linguistic analysis.
  \citet{Edwards2016} examined Australia, New Zealand and the UK, and
  found that changes were usually made by those responsible for creating
  the Hansard record, instead of the parliamentarians.} Earlier work on
the influence of parliaments, such as \citet{ZandenBuringhBosker2012},
often examined broader activity measures such as counts of sitting days.
This allowed for long time frames and wide comparisons. But analysing
Hansard records and their equivalents directly are an increasingly
viable and popular source of data as new methods and reduced
computational costs make larger-scale analysis easier, complementing
other measures.

The recent digitisation of the Canadian Hansard, \citet{BeelenEtc2017},
allowed \citet{RheaultCochran2018} to examine ideology and party
polarisation in Britain and Canada. In the UK, \citet{Duthie2016}
analysed Hansard records to examine which politicians made supportive or
aggressive statements toward other politicians between 1979 and 1990 and
\citet{PetersonSpirling2018} examined polarisation. And as digitisation
methods improve older UK records can be analysed, for instance
\citet{Dimitruk2018} considers the effect of estate bills on
prorogations in seventeenth century England. In New Zealand,
\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
and \citet{Graham2016} examined unparliamentary language between 1890
and 1950. And in the US \citet{GentzkowShapiroTaddy2018} examine
congressional speech records from 1873 to 2016 to find that partisanship
has risen in the past few decades.

@@

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
Additionally, there is a more limited set of XML records available in
some cases.\footnote{Tim Sherratt makes these XML records available as a
  single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through to today from Open Australia's website. The
  records can also be downloaded from the Australian Hansard website.}
We detail the sources of our Hansard PDFs in \ref{hansardsources} and
Appendix \ref{examplehansardpage} provides an example of what a Hansard
PDF looks like. There are 65,000 \textbf{{[}UPDATE{]}} days worth of
publicly available Hansard records across the state and federal
parliaments (Table \ref{tab:yearsusedtable}). Our data cleaning process
indicates concerns with a small number of PDFs and these are detailed in
Appendix \ref{knownhansardissues}.

@@

The formatting of the Hansard records changes between the different
parliaments and over time. We use scripts written in R (\citet{R2018})
to convert the PDFs into daily text records. An example of the workflow
and some reduced-detail scripts are provided in Appendix
\ref{hansardworkflow}. Some error is introduced at this stage because
many of the records are in a two-column format that need to be
separated, and the PDF parsing is not always accurate especially for
older records. An example of the latter issue is that `the' is often
parsed as `thc'. These errors are corrected when they occur at scale and
can be identified. The percentage of stop-words in each record is
reasonably consistent over time. This suggests that there is no
significant difference in the quality of the parsing over time. Details
of this process are provided in Appendix \ref{stopwordsgraph}.

These daily records are the main level that we consider in this paper,
but we also disaggregated them into individual-level records during the
cleaning process. Sometimes these are just short interjections or notes
that are not specific to any particular politician, such as `Honourable
members interjecting'. The high dimensional nature of text data means
that the appropriate level and focus of the dataset being analysed tends
to be specific to a research question. For instance, in our paper
interjections are not important because they do not usually contribute
much to defining the topics being discussed. But they are interesting in
their own right and \citet{Whyte2017} analysed them in a Canadian
context for the period 1926 to 2015 to find that female MPs were more
likely to be interrupted than male MPs.

Usually the disaggregation into individual-level records is done by
identifying politicians' names in particular patterns. For instance,
when Hansard is indicating that a particular person is speaking, as
opposed to being mentioned, often the name is in upper case, for
instance `Mr WHITLAM' or `Mr MENZIES'; followed by a dash or colon; or
are next to some title within brackets. There is substantial variation
in how the person making a statement is identified. Again some error is
introduced at this stage because of inconsistencies over time and
between the parliaments. There is considerable variance but on average
each daily record had 250 \textbf{{[}UPDATE{]}} individual-level
records, resulting in roughly 15 million rows \textbf{{[}UPDATE{]}}
across the state and federal parliaments.

Text is usually pre-processed before topic models are used. The specific
steps that we take are to remove numbers and punctuation and to change
the words to lower case. Then the sentences are deconstructed and each
word considered individually. \textbf{{[}Need to bundle\_ngrams i.e.~New
Zealand is new\_zealand.{]}}

@@

Data from other sources are needed to complement the parliamentary text
data. For instance, although the name, party, and division represented
are contained in Hansard records they are inconsistent. Also non-Hansard
information about the politicians informs our analysis. This includes:
date of birth and date of death; sex; date of entry to parliament and
exit from parliament; some aspects of their pre- and post-parliamentary
career; some aspects of their parliamentary career, such as ministry
appointments; and electoral information such as primary and
two-party-preferred results.

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments. However these had many
errors and were supplemented by data from the Australian Dictionary of
Biography and Wikipedia. The source for the electoral results is the
Australian Electoral Commission and Adam Carr's Australian Election
Archive. An example of the additional information is provided in
Appendix \ref{additionalinformation}.

@@

The main model that we use in this paper is the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage} and a Bayesian discrete choice
model. In a similar way to \citet{MuellerRauh2018}, we use topics to
analyse the effect of various events. In Appendix \ref{word2vec}, we
include an alternative approach that follows \citet{Taddy2015} by using
word2vec, which more closely uses words, rather than topics, as an
input.

The basis of the STM is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section we provide a brief overview of
both the LDA model and the STM. We consider the outputs of the topic
model as reduced dimension inputs that can be analysed within another
model. In our case they are inputs to a discrete choice model, and so we
then discuss that model.

@@

As applied to Hansard, the LDA method considers each statement to be a
result of a process where a politician first chooses the topics they
want to speak about. After choosing the topics, the speaker then chooses
appropriate words to use for each of those topics. More generally, the
LDA topic model works by considering each document as having been
generated by some probability distribution over topics. Similarly, each
topic could be considered a probability distribution over terms. To
choose the terms used in each document the speaker picks terms from each
topic in the appropriate proportion. Figures
\ref{fig:topicsoverdocuments} and \ref{fig:topicsoverterms} in Appendix
\ref{LDAexample} illustrates an example with five topics, two documents,
and ten terms.

@@

Gibbs sampling or the variational expectation-maximization algorithm can
be used to approximate the posterior. A summary of these approaches is
provided in Appendix \ref{LDAposteriorestimation}. The choice of the
number of topics, \emph{k}, drives the results and must be specified
\emph{a priori}. If there is a strong reason for a particular number,
then this can be used. Otherwise, one way to choose an appropriate
number is to use cross validation.

@@

We primarily implement the STM on the daily-level parliamentary text
data described earlier using the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. We consider both topic prevalence
and content to be functions of time. The choice of the number of topics
to use in the model is a situation-specific compromise. We use standard
diagnostic techniques with cross validation to decide on 80
\textbf{{[}UPDATE{]}} topics. More detail on this selection process is
available in Appendix \ref{selecttopicnumber}.

@@

We are interested in the effect of political, economic, and other events
on Australian parliamentary discussion. Political events are those
related to a change of government or an election. Economic events are
defined by substantial changes in various economic measures, such as the
onset of the Great Depression or the Great Recession. Other events are
those such as the 9/11 attacks, or the Bali Bombing. The full list of
events that we consider is detailed in Appendix
\citet{ref}(eventdetails).

@@

\section{Hansard details}\label{hansard-details}

\subsection{Hansard sources}\label{hansardsources}

{[}IS THIS BEING REFERENCED IN THE TEXT????{]}

\subsection{Example Hansard page}\label{examplehansardpage}

@@

\subsection{Known Hansard issues}\label{knownhansardissues}

The NSW Legislative Council was established earlier than 1856, however
the earlier Hansard records have not been through an independent OCR
process and were not used in this paper. However, the Google Tesseract
OCR engine as implemented by \citet{Ooms2018tesseract} provided useful
data and these could be used in the future.

@@

\caption{\label{tab:missingdays}Missing days}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rrrrr}
\toprule
year & HoR PDFs                      & Senate sitting days           & HoR sitting days              & HoR difference\\
\midrule
1902 & 106 & 93 & 107 & 1\\
1908 & 93 & 84 & 91 & -2\\
1909 & 97 & 71 & 98 & 1\\
1918 & 87 & 68 & 86 & -1\\
1920 & 113 & 76 & 114 & 1\\
\addlinespace
1921 & 92 & 79 & 93 & 1\\
1934 & 36 & 22 & 35 & -1\\
1935 & 54 & 37 & 55 & 1\\
1942 & 44 & 36 & 45 & 1\\
1948 & 89 & 39 & 90 & 1\\
\addlinespace
1951 & 55 & 40 & 56 & 1\\
1955 & 53 & 36 & 52 & -1\\
1974 & 64 & 64 & 62 & -2\\
1985 & 65 & 74 & 66 & 1\\
1991 & 66 & 83 & 67 & 1\\
\addlinespace
1992 & 60 & 76 & 44 & -16\\
1993 & 47 & 53 & 46 & -1\\
1994 & 69 & 80 & 68 & -1\\
1995 & 71 & 78 & 70 & -1\\
1997 & 79 & 82 & 76 & -3\\
\addlinespace
1998 & 56 & 57 & 54 & -2\\
2000 & 71 & 71 & 73 & 2\\
2002 & 68 & 60 & 69 & 1\\
2003 & 74 & 64 & 75 & 1\\
2004 & 58 & 49 & 59 & 1\\
2012 & 63 & 57 & 67 & 4\\
\bottomrule
\end{tabular}
\end{table}

Notes: Positive means I am missing some, Negative means I have too many.
Source:
\url{https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear}

\subsection{Example Hansard PDf to text record
workflow}\label{hansardworkflow}
